% This is a file that contains the tracking of the activities related to the project during the third week of March 2025.

\documentclass[12pt]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[backend=biber,style=numeric]{biblatex}
\usepackage[most]{tcolorbox}

\addbibresource{references.bib}

\begin{document}

\author{Joan Ronquillo}

\title{Project Progress - Week 3 of March 2025}
\maketitle

This is a file that contains the tracking of the activities
related to the Hydrodynamic Interactions project during the
third week of March 2025. The activities are divided into
groups and a summary of the progress is provided.

\section{Initial Status of the Project}
The project has made significant progress during the second week of March 2025. The key achievements include:
\begin{itemize}
    \item Interface of the \path{get_mobility_tensor} function has been updated and corrected.
    \item Preliminary structure of modules for the particle class has been established.
\end{itemize}
So far, the project is developing in some areas:
\begin{itemize}
    \item The development of the Python module with the implementation functions for mobility tensor calculations.
    \item The development of theory to express vectors in VSH basis.
    \item The initial functions to establish specific particle arrangements and geometries.
\end{itemize}

\section{Potential Tasks for the Week}
The following tasks are proposed for the week of March 10th to March 15th, 2025:
\begin{itemize}
    \item Check of the \path{setup.py} installing issues.
    \item Reading of Raúl's documents on software development.
    \item Exploration/creation of Python functions that allow specific particle arrays and geometries to be established.
    \item Exploration/creation of Python functions that handle vector spherical harmonics (VSH) and their properties. Study of the convenience of a class.
    \item Creation of Python functions that allow the mobility tensor to be obtained in the basis of VSH.
    \item Brenner's paper \cite{BRENNER1961242} reading.
\end{itemize}

\section{Week Progress}

\subsection{Wednesday, March 19th, 2025}
The week tasks and current progress have been reviewed. 

\subsection{Thursday, March 20th, 2025}
Raúl's documents on python packages development have been read.

\subsection{Friday, March 21st, 2025}
Based on Raúls's documents, the strcture of the
repository has been updated and checked. 
The dependencies have been updated in
\path{environment.yml}. The setup.py file has been
substituted by a pyproject.toml file, enabling 
developer mode installation. Metadata of the modules
and packages have been added. The particles module
has been modified with different classes for particle
and particle sets. Fundamental attributes and methods
have been added to the classes. The tests have been
updated to check the new classes.

\section{Summary}
The project has made significant progress during the
third week of March 2025. The key achievements include:
\begin{itemize}
    \item The repository structure has been updated and checked.
    \item The dependencies have been updated in \path{environment.yml}.
    \item The setup.py file has been substituted by a pyproject.toml file, enabling developer mode installation.
    \item Metadata of the modules and packages have been added.
    \item The particles module has been modified with different classes for particle and particle sets.
    \item Fundamental attributes and methods have been added to the classes.
    \item The tests have been updated to check the new classes.

\end{itemize}

\section {Current Status of the Project}
The project is developing in some areas:
\begin{itemize}
    \item The development of the Python module with the implementation functions for mobility tensor calculations.
    \item The development of theory to express vectors in VSH basis.
    \item The initial functions to establish specific particle arrangements and geometries.
\end{itemize}

\section{Next Steps}
The next steps for the project are:
\begin{itemize}
    \item Reading of Raúl's documents on GitHub basics.
    \item Studying the convenience of class/functions for particle arrangements and geometries.
    \item Exploration/creation of Python functions that allow specific particle arrays and geometries to be established.
    \item Exploration/creation of Python functions that handle vector spherical harmonics (VSH) and their properties. Study of the convenience of a class.
    \item Creation of Python functions that allow the mobility tensor to be obtained in the basis of VSH.
    \item Reading of Brenner's paper \cite{BRENNER1961242}.
\end{itemize}

\printbibliography

\end{document}
