% This is a file that contains the tracking of the activities related to the project during the first week of March 2025.
% The activities are divided into groups and a summary of the progress is provided.

\documentclass{article}

\usepackage{graphicx}
\usepackage{dirtree}

\begin{document}
\author{Joan Ronquillo}

\title{Project Progress - Week 1 of March 2025}
\maketitle

This is a file that contains the tracking of the activities related to the Hydrodynamic
Interactions project during the first week of March 2025.The activities are divided into
groups and a summary of the progress is provided.

\section{Initial Status of the Project}
The project has made significant progress up until the first week of March 2025. The key achievements include:

\begin{itemize}
    \item Meetings with Raúl to discuss the hydrodynamic interactions.
    \item Documentation in Notion of the basic theory behind hydrodynamic interactions.
    \item Preliminary exploration of the "spreadinterp" repository.
    \item Creation of a general function to obtain the mobility tensor given a solver and a set of particle positions.
    \item Initial tests for obtaining the "Self-Mobility Tensor".
\end{itemize}

\section{Potential Tasks for the Week}
The following tasks have been identified as potential areas of focus for the first week of March 2025:
\begin{itemize}
    \item Development of the Python module with the implementation functions.
    \item Tests for obtaining the RPY tensor. Discussion of the representation and its properties.
    \item Initial functions to establish specific particle arrangements and geometries.
\end{itemize}

\section{Week Tracking}
\subsection{Monday - March 3, 2025}
The repository has been reorganized, and the functionalities of the gitignore, setup.py, 
and \_\_init\_\_.py files have been discussed to manage the import of functions and modules. 
The use of pytest and the inclusion of asserts in the test functions are emphasized. 
The correct functioning of the self-mobility tensor test is verified.

\subsection{Tuesday - March 4, 2025}
I have been learning how to compile LaTeX projects located inside the repository.
The pdf tab viewer in VSCode has been installed and configured to facilitate the 
visualization of the documents. This document serves as an example of the compilation 
process.

\subsection{Wednesday - March 5, 2025}
The tasks for the week have been specified and the progress in documentation, code, and testing has been tracked.

\section{Current Next Steps}
The next steps for the project include:
\begin{itemize}
    \item An script that obtains the RPY mobility for two particles as a function of the distance between them.
    \item Development of the Python module with the implementation functions.
    \item Tests for obtaining the RPY tensor. Discussion of the representation and its properties.
\end{itemize}
\end{document}


